Explain urban regional function

### 2018-11-10 paper.tex

\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis.}
\end{abstract}
%

\section{Introduction}

\subsection{motivation}
%urban computing
Urban computing, defined in~\cite{Zheng2014UrbanConcepts} as a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces.%definition
One of the most important data source is human mobility data, e.g. pick-ups and drop-offs of taxicabs.
Such mobility data can contribute to improve living quality of residents, e.g. optimizing urban planning~\cite{Zheng2011taxicabs}, easing traffic congestion~\cite{Meng2017Traffic}, decreasing energy consumption ~\cite{Zhang2015Fuel}, reducing air pollution~\cite{Shang2014Pollution} and so on.
Therefore, mining and modeling mobility data has attracted attentions from both academia and industry.

@@

%explain implementation, we need to incorporate activity and online sentiment
In this paper,to make the results more convinced, we build a system that provides explanations for our functional region clustering results.
We build our system upon two data sets. One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
We combined the urban computing using mobility data with sentiment analysis using geo-content.
As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we learn/highlight/assign the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

@@

\subsection{challenge}
In order to solve the problem,we face two challenges.

The first one of it is to extract the urban feature from comment data.Urban feature is a set of attributes that could describe characters of the Corresponding region,e.g. traffic,noise,neighbors and so on.
Part of our content data comes from social media without detailed coordinates.They are full of sentiment tendencies but have difficulty to induced to a particular region.
The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.Due to the case,existing sentiment extraction model Sentires~\cite{Zhang2015Sentires} are infeasible in our models.%urban feature
In order to get the location information from these content data,we....

And the second challenge is that find the function of region is changing with time.The former research regarded time as a distinctive attribute of the region,put it as an input of DRoF model instead of describe its change~\cite{Yuan2012FunctionRegion}.%zheng 's time

%function = distribution of activitys and opinions

%previous research

%opinion

Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of user.
  \item We combined the sentiment and human mobility as explanation,find the urban feature within a region.
  %\item 3
\end{itemize}

The remainder of the paper is organized as follows.
We give an overview for related work in Section 2.
In Section 3, we introduce our novel models as well as proving their logic.
Section 4 presents the suprior result in experiments of our models.
Finally, we made a conclusion and looked forward to our future work in Section 5.

@@

%extract the different among these data
The simplest form of mobility data is check-ins data, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
Statistical association analysis is commonly conducted on check-ins. For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers’ refueling decision~\cite{Zhang2015Fuel}.

The second form of mobility data is origin-destination pairs, i.e. a pick-up point and a drop-off point of a taxi trajectory.
Clustering methods including Newman modularity cluster algorithm~\cite{Newman2004ModularityFunction} are applied in functional region identification~\cite{Ratti2010Telecom}.
Recently, latent factor models are proposed to treat a region as document and infer functional-specific ~\cite{Yuan2012FunctionRegion}.%
Latent activity is imported in topic model in~\cite{Yuan2015FunctionRegion} to define the specific functions of different regions.

Alternatives for origin-destination pairs are trajectory data.
Applications on trajectory data include recommendation, e.g. to recommend more suitable place to drivers~\cite{Ge2011TaxiBusiness,Garg2018Route} and traffic planning, e.g. to find reachable region within a given temporal period~\cite{Wu2017Reachable}, %find a fast route
or to predict travel time~\cite{Wang2018Deep}.

@@

\iffalse
\section{Application}
Our models have a wide range of application and their value
\subsection{Billboard}
Billboard
\subsection{Trajectory}
\fi

@@

\subsection{Preparation}

@@

\subsection{Evaluation Metrics}

@@

\section{Conclusion}
In this paper , we proposed several models to find the most possible destination region for users and add explanation for it to enhance its persuasiveness.
The models have improve some extra recognition accuracy ,which have an extra contribution for functional city.

@@

\bibitem{Garg2018Route}Garg, N.; Ranu, S. Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer! Proceedings of the 24th ACM SIGKDD International Conference on Knowledge Discovery \& 38; Data Mining,ACM,2018, 1425-1434

@@

\bibitem{Zhang2018SIGIR} Zhang, Y.; Zhang, Y.; Zhang, M. SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018) //The 41st International ACM SIGIR Conference on Research \& 38; Development in Information Retrieval,ACM,2018, 1411-1413

@@

\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. 2018.

@@

@@

\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems,2018

>>>>

\begin{abstract}
How to identify different functional regions and give them reliable explanations are the main objectives of this work.

(15--250 words.)

\keywords{Explanation  \and Urban computing \and Online content \and Sentiment analysis \and Latent Factor \and Matrix Factorization.}
\end{abstract}
%

\section{Introduction}
\textbf{Motivation.}
%urban computing
Urban computing, defined in~\cite{Zheng2014UrbanConcepts} as a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces.%definition
One of the most important data source is human mobility data, e.g. pick-ups and drop-offs of taxicabs.
Such mobility data can contribute to improve living quality of residents, e.g. optimizing urban planning~\cite{Zheng2011taxicabs}, easing traffic congestion~\cite{Meng2017Traffic}, decreasing energy consumption ~\cite{Zhang2015Fuel}, reducing air pollution~\cite{Shang2014Pollution} and so on.
Therefore, mining and modeling mobility data has attracted attentions from both academia and industry.

@@

%explain implementation, we need to incorporate activity and online sentiment
In this paper,to make the results more convincing, we build a system that provides explanations for our functional region clustering results.
We build our system upon two data sets. One is mobility data 3 million including pick-up and drop-off coordinates and time,which provide detailed moving pattern for the dynamic urban system to discovering regions with different functions.
And the other is comment data with shop address that reveal sentiment tendencies of the shop.We could exact labels as the form of 'character-opinion-sentiment' from and pick labels with strongest sentiment as our explanation.
We combined the urban computing using mobility data with sentiment analysis using geo-content.
As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we learn/highlight/assign the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

@@

\textbf{Challenge.}
In order to solve the problem,we face two challenges.

The first one of it is to extract the urban feature from comment data.
Urban feature is a set of characters with special geographical attributes, e.g., traffic, noise, neighbors and so on.
Part of our content data comes from social media without detailed coordinates.They are full of sentiment tendencies but have difficulty to induced to a particular region.
The rest are comments of shops with the shop address.The feature extracted from it is more related to shop feature than urban feature.
Due to the scenario, existing sentiment extraction model ~\cite{Lu2011Label} can not be used directly in our models.%urban feature
In order to get the location information from these content data, features with typical urban scene are selected from all features extracted by a toolkit called Sentires~\cite{Zhang2015Sentires}.
These selected urban feature

And the second challenge is how to explain the features.
If the extracted urban features used for explanations can not correspond to the labeled activity used to identify functional regions, the explanations will not persuasively explain the reasons for the identification, or even will not be generated.

\textbf{Contribution.}
Our paper has an outstanding result in following several aspect:
\begin{itemize}
  \item To the best of our knowledge,we are the first to give explanation to urban functional region identification , which could improve the trustiness and satisfaction of user.
  \item We combined the sentiment and human mobility as explanation,find the urban feature within a region.
  \item The explanation is given by latent factor model. We use matrix factorization to decrease the sparseness of matrix.
\end{itemize}

\textbf{Structure.}
The remainder of the paper is organized as follows.
We give an overview for related work in Section 2.
In Section 3, we introduce our novel framework as well as proving their feasibility.
Section 4 presents the superior result in experiments of our models.
Finally, we made a conclusion and looked forward to our future work in Section 5.

@@

%extract the different among these data
The simplest form of mobility data is \textbf{check-ins data}, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
Statistical association analysis is commonly conducted on check-ins. For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers’ refueling decision~\cite{Zhang2015Fuel}.

The second form of mobility data is \textbf{origin-destination pairs}, i.e. a pick-up point and a drop-off point of a taxi trajectory.
Clustering methods including Newman modularity cluster algorithm~\cite{Newman2004ModularityFunction} are applied in functional region identification~\cite{Ratti2010Telecom}.
Recently, latent factor models are proposed to treat a region as document and infer functional-specific ~\cite{Yuan2012FunctionRegion}.%
Latent activity is imported in topic model in~\cite{Yuan2015FunctionRegion} to define the specific functions of different regions.

Alternatives for origin-destination pairs are \textbf{trajectory data}.
Applications on trajectory data include recommendation, e.g. to recommend more suitable place to drivers~\cite{Ge2011TaxiBusiness,Garg2018Route} and traffic planning, e.g. to find reachable region within a given temporal period~\cite{Wu2017Reachable}, %find a fast route
or to predict travel time~\cite{Wang2018Deep}.

@@

\subsection{Explanation for Complex Models}

\section{System Overview}
We proposed a novel framework to make an explanation for the functional region identification.

\section{Urban Feature Extraction}

\section{Explanation Model}
%relationship between latent factor model and matrix factorization

$$R=b_u+U^TV+\beta()$$

\subsection{Functional Region Identification}

%clustering
%input:trajectory
%output:a matrix of activity-location

\subsection{Preliminary: Latent Factor Model and Matrix factorization}

To identify different functional region,we need to train a model

%what is latent factor

%what is kernel function

kernel function is a method that map low-dimension data into high-dimension data.It

%we plans models to combine latent factor

%what is the target of this model

%what is matrix factorization

%in our framework, what is the detail meaning of latent factorization

\subsection{Preliminary: Kernel Function}
%what is kernel function

%its application on recommendation system

%how to define out matr

@@

\subsection{Preparation}
To form the basic region of city,we segment the urban area of city into region units by the major road network and make a map simplification.
The longitude of map range is [103.93,104.21] and latitude range is [30.56,30.79], which covers the main area of a city.
Raster-based model is more computationally efficient and succinct for territorial analysis, which is suitable for our map scenario.
We downloaded the major road network of this region\footnote{http://www.bigemap.com/} and rasterized the area into a 2000 $\times$ 2400 grid.
In the grid, the road network is converted to a binary image, as 1 stands for the road while 0 stands for the blank areas.

The main road data is present in Fig.\ref{raw_map}, including motorway, trunk, primary, secondary, tertiary and their links.
But the Fig.\ref{raw_map} is full of some unnecessary details, such as the lanes of a road and the overpasses, which disturb the distribution of regions.
As explained in~\cite{Yuan2015FunctionRegion}, the dilation and thinning process are operated on the original road data to remove these details and simplify the map.
\begin{figure}
\centering
\subfigure[Original segment of city]{
\label{raw_map} %% label for first subfigure
\includegraphics[width=1.5in]{chengdu_1.png}}
\subfigure[After dilation operator]{
\label{dilation} %% label for second subfigure
\includegraphics[width=1.5in]{chengdu_2.png}}
\subfigure[After thinning operator]{
\label{thinning} %% label for second subfigure
\includegraphics[width=1.5in]{chengdu_3.png}}
\caption{The preparation process of road network}
\label{dilation and thinning} %% label for entire figure
\end{figure}

@@

\subsection{Evaluation Metrics}
We evaluate the functional region through two approaches. One is the percentage of regions that could find explanation label by our framework; while the other is the quality and accuracy of the explanation given by our framework.

For the first approach, we define the percentage of explainable region as follow:
$$explanation\ percentage=\frac{|regions\ with\ explanation\ label|}{|all\ regions|}$$

For the second approach,

@@

\section{Conclusion}
Function regions identification is an important part of urban computing.
But the relative research lack of persuasive explanation.
In this paper, we proposed a novel framework to give persuasive explanation for functional regions identification.
 %to enhance its persuasiveness.

@@

\bibitem{Garg2018Route}Nandani Garg and Sayan Ranu. Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!. In KDD ’18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19–23, 2018, London, United Kingdom. 2018.

@@

\bibitem{Zhang2018SIGIR}Yongfeng Zhang, Yi Zhang, and Min Zhang. SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018). In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR ’18). 2018.

@@

\bibitem{Zhang2018Survey} Zhang Y, Chen X. Explainable Recommendation: A Survey and New Perspectives[J]. arXiv preprint arXiv:1804.11192. 2018.

@@

    Zhang Y, Lai G, Zhang M, et al. Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval. ACM, 2014:83-92.

@@

\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems. In Proceedings of the First International Workshop on Comprehensibility and Explanation in AI \& ML, 2017.
\bibitem{Lu2011Label}Lu Y, Castellanos M, Dayal U, et al. Automatic construction of a context-aware sentiment lexicon:an optimization approach[C]// International Conference on World Wide Web, WWW 2011, Hyderabad, India, March 28 - April. DBLP, 2011:347-356.
